---
title: "dplyr filter homework"
author: "Vassili Kiritsenko"
date: "2019-03-12"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Exercises

Loading required libraries:
```{r}
library(tidyverse)
library(here)
```

Importing dataset:
```{r}
viruses <- read_csv(here("data", "viruses.csv"))
```

Print out dataset:
```{r}
viruses
```


1. Find all viruses that:

- have genome of over 10000kb

```{r}
filter(viruses, size_kb>10000)
```

- belong to *Papillomaviridae*

```{r}
filter(viruses, subgroup=='Papillomaviridae')
```

- are from plants and environment

```{r}
filter(viruses, host %in% c('plants','environment'))
```

- were released between 01. January 1980 - 01. January 1990, including these days:

```{r}
library(lubridate)
filter(viruses,  date(release_date) >= date('1980-01-01') & date(release_date) <= date('1990-01-01'))

```

2. there is also between() function in dplyr. 

What does it do? Run ?between
How can you use it to find viruses with genomes between 1 to 2 kb?

```{r}
filter(viruses, between(size_kb, 1000, 2000))
```

3. Find Enteroviruses:

Hint: use str_detect()
```{r}
filter(viruses, str_detect(organism_name, 'nterovirus'))
```

